---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Project data was supplied as a aip file `activity.zip` which was unzipped
manually to yield `activity.csv`.

```{r loading}
data <- read.csv("activity.csv")

#  Just a simple comment.
#` A backticked comment
#' An SQUOTEd comment
```

## What is mean total number of steps taken per day?


```{r histogram}
require{dplyr}
require(ggplot2)

stepsPerDay      <- aggregate(data=data, steps ~ date, FUN = sum)
stepsPerDay$date <- as.Date(stepsPerDay$date)

ggplot(data=stepsPerDay, aes(steps)) 	           + 
    xlab('Steps per Day') 		           + 
    ylab('Number of Days with That Number of Steps')	   +
    ggtitle('Steps per Day in Period of Interest') + 
    geom_histogram(bins=100)

```

The figure above shows how many days in the period of interest have step 
counts in various buckets.

```{r meanAndMedian} 
meanStepsPerDay  <- mean(stepsPerDay$steps)
medianStepsPerDay <- median(stepsPerDay$steps)

```

We can see from the above that the mean number of steps per day is
`r sprintf("%.0f", meanStepsPerDay)` and the median is `r medianStepsPerDay`.

## What is the average daily activity pattern?

```{r dailyActivity}

data          <- mutate(data, hour = as.integer(0.001 + interval / 100))
data$interval <- (data$interval %% 60) / 5
data          <- select(date, hour, interval, steps)

data$date     <- as.factor(data$date)
data$hour     <- as.factor(data$hour)
data$interval <- as.factor(data$interval)	# steps in 5-minute period

# This is now tidy and in the long form.

aggData       <- group_by(data=data, date, hour, interval) %>% 
                     summarise(stepsInInterval=sum(steps)



```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
